Output Summary

### 2023-05-04 03-post-process/output-plots-children/11-noise-term-diags.Rmd
Consistency updates: 11-noise-term-diags.Rmd

oma_labels = function(xlab = "", ylab = "", xline = 0.75, yline = 0.75, ...) {
  mtext(side = 1, outer = TRUE, line = xline, text = xlab, ...)
  mtext(side = 2, outer = TRUE, line = yline, text = ylab, ...)
}

no_data_plot = function(main = NULL) {
  plot(1,1, xlim = c(-1,1), ylim = c(-1,1), type = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = main)
  text(0,0, "No Data", font = 3)
}

my_par = function() {
  par(mfrow = c(2,2), mar = c(1,1,2,2), oma = c(2,2,0,0), tcl = -0.15, mgp = c(2,0.35,0))
}
```

@@

  # blank plot with correct dimensions
  par(lend = "square")
  plot(qresid["mean",] ~ all_yrs[y_ind], main = main, type = "n",
       ylim = ylim, xlim = range(all_yrs[y_ind]), xaxt = "n", yaxt = "n", xlab = "", ylab = "")

@@

  # draw posterior mean for first and half of time series
  lines(x = all_yrs[y_ind[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
  lines(x = all_yrs[y_ind[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)

  # draw the noise time series: mean and 95% CRI
  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "salmon")
  segments(all_yrs[observable], qresid["25%",], all_yrs[observable], qresid["75%",], col = "salmon", lwd = 4)
  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = "salmon", cex = 1.25)

  # draw legend that shows estimate summaries
  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
  box()

@@

#### Egg-to-Parr Survival

```{r egg-to-parr-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_E_Pb_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Egg-to-Parr Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Summer Parr Mean Length

```{r summer-length-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lL_Pb_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Summer Parr Mean Length) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pi-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,LH_type,pop]", pop = j, main = pops[j], LH_type = i_fall))
oma_labels("Brood Year", "logit(Proportion Fall Migrants) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r overwinter-surv-noise-fall, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 1, main = pops[j]))
oma_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r overwinter-surv-noise-spring, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 2, main = pops[j]))
oma_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Summer Parr to Spring Smolt "Growth Factor"

```{r growth-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lDelta_L_Pb_Mb_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Summer to Spring Growth Factor) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Trib to LGR {.tabset .tabset-pills}

@@

```{r trib-to-LGR-surv-nor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,LH_type,origin,pop]", pop = j, origin = 1, LH_type = 2, main = pops[j]))
oma_labels("Brood Year", "logit(Trib to LGR Survival [NOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r trib-to-LGR-surv-hor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,LH_type,origin,pop]", pop = j, origin = 2, LH_type = 2, main = pops[j]))
oma_labels("Brood Year", "logit(Trib to LGR Survival [HOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### LGR to BON Survival

```{r LGR-to-BON-surv-noise, fig.width = 6, fig.height = 3.5}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r yr1-ocean-surv-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, year = c(ts_yrs), pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(First Year Ocean Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-3-nor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-3 [NOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-3-hor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-3 [HOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-4-nor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-4 [NOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-4-hor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-4 [HOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

#### BON to LGR Survival

```{r BON-to-LGR-surv-noise, fig.width = 6, fig.height = 3.5}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Rb_Ra_qresid[year,origin]", origin = o, main = origins[o]))
oma_labels("Return Year", "logit(BON to LGR Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r prespawn-surv-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Sb_Sa_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Return Year", "logit(Pre-spawn Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

  # blank plot with correct dimensions
  par(lend = "square")
  plot(qresid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "",yaxt = "n")

@@

  # draw the noise time series: mean and 95% CRI
  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "salmon")
  segments(all_yrs[observable], qresid["25%",], all_yrs[observable], qresid["75%",], col = "salmon", lwd = 4)
  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = "salmon", cex = 1.25)

@@

  # draw posterior mean for first and half of time series
  lines(x = all_yrs[observable[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
  lines(x = all_yrs[observable[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)

  # draw legend that shows estimate summaries
  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
  box()

@@

```{r fall-trap-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lPa_obs_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Fall Parr Abundance) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r spring-trap-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lMb_obs_qresid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Spring Trap Count) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r adult-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lRa_obs_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Return Year", "log(Total Adult Count) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

#### Summer Parr $\rightarrow$ LGR

```{r summer-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pb_Ma_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Summer Tagging to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Fall Parr $\rightarrow$ LGR

```{r fall-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Fall Tagging to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Winter Parr $\rightarrow$ LGR

```{r winter-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) {
  if (j == 3) {
    no_data_plot(main = pops[j])
  } else {
    plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
  }
})
oma_labels("Brood Year", "logit(Winter Tagging to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}

@@

```{r spring-surv-resid-nor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
oma_labels("Brood Year", "logit(NOR Smolt to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r spring-surv-resid-hor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) {
  if (j == 3) {
    no_data_plot(main = pops[j])
  } else {
    plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
  }
})
oma_labels("Brood Year", "logit(HOR Smolt to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### LGR Smolt $\rightarrow$ Ocean

```{r hydro-surv-resid, fig.width = 6, fig.height = 3.5}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("Lphi_obs_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r bon-adult-surv-resid, fig.width = 6, fig.height = 3.5}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("x_LGR_obs_qresid[year,origin]", origin = o, main = origins[o]))
oma_labels("Return Year", "Count of PIT Tagged Adults at LGR Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r pre-spawn-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("x_carcass_spawned_obs_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Return Year", "Count of Female Spawned-out Carcasses Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

#### Summer Length

```{r summer-length-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Pb_obs_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Mean Summer Length) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Spring Length

```{r spring-length-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Mb_obs_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Mean Spring Length) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

weir_comp_qresid_plots = function(j) {
  my_par(); par(mfrow = c(2,3))
  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Ra_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Ra[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
  oma_labels("Return Year", "Weir Age/Origin Composition Residual")
  do.call(rbind, tmp)
}
```

>>>>

no_data_plot = function(main = NULL) {
  plot(1,1, xlim = c(-1,1), ylim = c(-1,1), type = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = main)
  text(0,0, "No Data", font = 3)
}
```

@@

  # blank plot with correct dimensions
  plot(qresid["mean",] ~ all_yrs[y_ind], type = "n",
       ylim = ylim, xlim = range(all_yrs[y_ind]), xaxt = "n", yaxt = "n", xlab = "", ylab = "")

@@

  # draw posterior mean for first and half of time series
  lines(x = all_yrs[y_ind[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = main_cols["model2"], lty = 3, lwd = 2)
  lines(x = all_yrs[y_ind[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = main_cols["model2"], lty = 3, lwd = 2)

  # draw the noise time series: mean and 95% CRI
  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = main_cols["model"])
  segments(all_yrs[observable], qresid["25%",], all_yrs[observable], qresid["75%",], col = main_cols["model"], lwd = 4)
  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "white", bg = "white", cex = 1.25)
  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = main_cols["model"], bg = tran_cols["model"], cex = 1.25)

  # draw legend that shows estimate summaries
  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
  rect(usr[1], 1, usr[2], usr[4], border = par("col.axis"), col = "grey95")
  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, text.col = par("col.axis"), legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
  box(col = par("col.axis"))
  panel_label(main, "topright")

@@

#### Egg $\to$ Parr Survival

```{r egg-to-parr-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_E_Pb_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Egg \u2192 Parr Survival) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Parr Mean Length

```{r summer-length-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lL_Pb_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "log(Summer Parr Mean Length) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pi-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,LH_type,pop]", pop = j, main = pops[j], LH_type = i_fall))
axis_labels("Brood Year", "logit(Proportion Fall Migrants) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r overwinter-surv-noise-fall, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 1, main = pops[j]))
axis_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r overwinter-surv-noise-spring, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 2, main = pops[j]))
axis_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Parr $\to$ Smolt "Growth Factor"

```{r growth-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lDelta_L_Pb_Mb_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "log(Parr \u2192 Smolt 'Growth' Factor) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Trib $\to$ LGR {.tabset .tabset-pills}

@@

```{r trib-to-LGR-surv-nor, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,LH_type,origin,pop]", pop = j, origin = 1, LH_type = 2, main = pops[j]))
axis_labels("Brood Year", "logit(Trib \u2192 LGR Survival [NOR]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r trib-to-LGR-surv-hor, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,LH_type,origin,pop]", pop = j, origin = 2, LH_type = 2, main = pops[j]))
axis_labels("Brood Year", "logit(Trib \u2192 LGR Survival [HOR]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### LGR $\to$ BON Survival

```{r LGR-to-BON-surv-noise, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
axis_labels("Brood Year", "logit(LGR \u2192 BON Survival) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r yr1-ocean-surv-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, year = c(ts_yrs), pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Yr1 Ocean Survival) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-3-nor-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Mature at Age-3 [NOR]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-3-hor-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Mature at Age-3 [HOR]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-4-nor-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Mature at Age-4 [NOR]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-4-hor-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Mature at Age-4 [HOR]) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

#### BON $\to$ LGR Survival

```{r BON-to-LGR-surv-noise, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Rb_Ra_qresid[year,origin]", origin = o, main = origins[o]))
axis_labels("Return Year", "logit(BON \u2192 LGR Survival) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r prespawn-surv-noise, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Sb_Sa_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Return Year", "logit(Pre-spawn Survival) QResidual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

  # blank plot with correct dimensions
  plot(qresid["mean",] ~ all_yrs[observable], type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "",yaxt = "n")

@@

  # draw the noise time series: mean and 95% CRI
  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = main_cols["model"])
  segments(all_yrs[observable], qresid["25%",], all_yrs[observable], qresid["75%",], col = main_cols["model"], lwd = 4)
  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "white", bg = "white", cex = 1.25)
  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = main_cols["model"], bg = tran_cols["model"], cex = 1.25)

@@

  # draw posterior mean for first and half of time series
  lines(x = all_yrs[observable[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = main_cols["model2"], lty = 3, lwd = 2)
  lines(x = all_yrs[observable[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = main_cols["model2"], lty = 3, lwd = 2)

  # draw legend that shows estimate summaries
  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
  rect(usr[1], 1, usr[2], usr[4], border = par("col.axis"), col = "grey95")
  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, text.col = par("col.axis"), legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
  box(col = par("col.axis"))
  panel_label(main, "topright")

@@

```{r fall-trap-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lPa_obs_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "log(Fall Parr Abundance) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r spring-trap-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lMb_obs_qresid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "log(Spring Trap Count) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r adult-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lRa_obs_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Return Year", "log(Total Adult Count) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

#### Summer Parr $\to$ LGR

```{r summer-surv-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pb_Ma_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Summer Parr \u2192 LGR Survival) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Fall Parr $\to$ LGR

```{r fall-surv-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
axis_labels("Brood Year", "logit(Fall Parr \u2192 LGR Survival) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Winter Parr $\to$ LGR

```{r winter-surv-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) {
  if (j == 3) {
    no_data_plot(main = pops[j])
  } else {
    plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
  }
})
axis_labels("Brood Year", "logit(Winter Parr \u2192 LGR Survival) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Spring Smolt $\to$ LGR {.tabset .tabset-pills}

@@

```{r spring-surv-resid-nor, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
axis_labels("Brood Year", "logit(NOR Smolt \u2192 LGR Survival) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r spring-surv-resid-hor, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) {
  if (j == 3) {
    no_data_plot(main = pops[j])
  } else {
    plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
  }
})
axis_labels("Brood Year", "logit(HOR Smolt \u2192 LGR Survival) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### LGR Smolt $\to$ BON

```{r hydro-surv-resid, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("Lphi_obs_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
axis_labels("Brood Year", "logit(LGR \u2192 BON Survival) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r bon-adult-surv-resid, fig.width = 6, fig.height = 3.5}
mypar(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("x_LGR_obs_qresid[year,origin]", origin = o, main = origins[o]))
axis_labels("Return Year", "Count of PIT Tagged Adults at LGR QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r pre-spawn-surv-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("x_carcass_spawned_obs_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Return Year", "Count of Female Spawned-out Carcasses QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

#### Parr Mean Length

```{r summer-length-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Pb_obs_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "log(Parr Mean Length) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Smolt Mean Length

```{r spring-length-resid, fig.width = p4_width, fig.height = p4_height}
mypar()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Mb_obs_qresid[year,pop]", pop = j, main = pops[j]))
axis_labels("Brood Year", "log(Smolt Mean Length) QResidual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

weir_comp_qresid_plots = function(j) {
  mypar(mfrow = c(2,3))
  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Ra_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Ra[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
  axis_labels("Return Year", "Weir Age/Origin Composition QResidual")
  do.call(rbind, tmp)
}
```
